### 2023-03-16 outputs/output.qmd
Updated outputs folder to include Quarto document

---
title: "Well-being of Individuals from the United States Global Social Survey are Affected by Finances, Relationships, and Health"
author: "Justin Abando, Jin Di Liu, Marcin Jaczynski"
thanks: "Code and data are available at: https://github.com/jackchinski/happiness_report"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "DON'T FORGET THIS"
format: pdf
bibliography: references.bib
---

```{r}
#| include: false

knitr::opts_chunk$set(echo=TRUE)

###Workplace Setup###
library(tidyverse)
library(dplyr)
library(ggplot2)

```

# Introduction

# Data Source

# Data Gathering

# Results

```{r}
#| label: fig-satfincome
#| fig-cap: Visualization of...
#| echo: false

ggplot( 
  clean5, aes(
    x = new_income_range, fill = satfin)) + 
  geom_bar(
    position = "stack") + #Creating a stacked bar plot
  theme_minimal() + #Using a simple theme
  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
    angle = 60, 
    hjust = 1)) + 
  labs(x = "Income Ranges", #Labeling the axes and fill section
       y = "Frequency",
       fill = "Financial Satisfaction")

```

# Discussion

# Appendix

### 2023-03-16 outputs/output.qmd
Updated .qmd and inputs folder to include .csv to be read into Quarto doc

@@
 
+quartoclean5 <- read_csv("../inputs/data/clean5.csv")
+
 ```
@@
 ggplot( 
-  clean5, aes(
+  quartoclean5, aes(
     x = new_income_range, fill = satfin)) + 

### 2023-03-16 scripts/02-data_cleaning.R

@@ -82,12 +82,15 @@ rm(master_clean4)
 ##master_clean5 groups all the cleaned incomes in 5 ranges: . This helps us better
 ##represent the data later in the analysis
 
+write.csv(clean5, "inputs/data/clean5.csv")
+
 master_clean5$new_income_range <- ifelse(master_clean5$income16 %in% c("UNDER $1 000", "$1 000 TO 2 999", "$3 000 TO 3 999", "$4 000 TO 4 999", "$5 000 TO 5 999", "$6 000 TO 6 999",
                                                          "$7 000 TO 7 999", "$8 000 TO 9 999"), "0 to 9 999",
                                   ifelse(master_clean5$income16 %in% c("$10000 TO 12499", "$12500 TO 14999", "$15000 TO 17499", "$17500 TO 19999"), "10 000 to 19 999",
                                          ifelse(master_clean5$income16 %in% c("$20000 TO 22499", "$22500 TO 24999", "$25000 TO 29999", "$30000 TO 34999", "$35000 TO 39999"), "20 000 to 39 999", 
                                                 ifelse(master_clean5$income16 %in% c("$40000 TO 49999", "$50000 TO 59999", "$60000 TO 74999", "$75000 TO $89999"), "40 000 to 89 999", 
                                                        ifelse(master_clean5$income16 %in% c("$90000 TO $109999", "$110000 TO $129999", "$130000 TO $149999", "$150000 TO $169999", "$170000 OR OVER"), "90 000 to 170 000", "other")))))
+
 
 # master_clean8 reduced the num of entires to 1745 from 3496. This will be
 # used to represent data on married and interpretable respondents.

### 2023-03-16 scripts/02-data_cleaning.R
Added changes to data cleaning so it makes correct outputs, and moved files to correct locations

@@ -116,8 +116,13 @@ master_clean10 <- subset(master_clean5, health != ".s:  Skipped on Web")
 # because it represents both married, unmarried, or skipped entries respondents.
 master_clean11 <- subset(master_clean5, happy != ".s:  Skipped on Web")
 
+## Output all of our datasets in usable csvs.
 
-
+write.csv(master_clean5, "outputs/data/master_cleaned.csv")
+write.csv(master_clean8, "outputs/data/hapmar_cleaned.csv")
+write.csv(master_clean9, "outputs/data/finalter_cleaned.csv")
+write.csv(master_clean10, "outputs/data/health_cleaned.csv")
+write.csv(master_clean11, "outputs/data/happy_cleaned.csv")
 
 
 

### 2023-03-16 outputs/paper/paper3.qmd
Updated quarto doc

--- 2023-03-16 outputs/output.qmd
@@
 
-quartoclean5 <- read_csv("../inputs/data/clean5.csv")
+quartoclean5 <- read_csv("../../inputs/data/clean5.csv")
 
@@
 
-# Introduction
+# 1 Introduction
 
-# Data Source
+# 2 Data
 
-# Data Gathering
+## 2.1 Tools Used
 
-# Results
+## 2.2 Survey Methodology
+
+## 2.3 Survey Biases and Ethics
+
+## 2.4 Data Collection
+
+## 2.5 Data Cleaning
+
+# 3 Results
+
+\newpage
 
@@
 #| label: fig-satfincome
-#| fig-cap: Visualization of...
+#| fig-cap: Visualization of financial satisfaction of respondents with respect to their relative income.
+There is a larger proportion of respondents that claim that they are not satisfied with their finances at lower income ranges.
+As the income range increases, more respondents proportionally express that they are either more of less satisfied, or are pretty well satisfied with their financial situation.
 #| echo: false
@@
 
-# Discussion
+# 4 Discussion
 
-# Appendix
+## 4.1 Limitations
+
+# 5 Appendix

### 2023-03-16 inputs/readme_rawdata.Rmd

---
title: "readme_rawdata"
author: "Jin Di Lu"
date: "2023-03-16"
output: html_document
---
## Raw Data Acquision readme
(Preface: this process requires access to an internet browser, a file compression software such as 7zip, and Microsoft Excel.)

In order to acquire the GSS data through legal means, follow these precise steps in order to obtain the dataset we worked with.

1. Access the GSS Data Explorer website at: https://gssdataexplorer.norc.org/home

2. Register for an account at the GSS Data Explorer website by clicking on register.

3. Afterwards, input the necessary information needed to successfully register.

4. Accept the required confirmation email and then access to the data explorer will be granted to you.

5. After accepting the confirmation email, return to the GSS Data Explorer website and log in with your credentials

6. After logging in, access the Data Explorer search function and add variables Year, id, ballot, happy, satfin, hapmar, income16, health, life, finalter to the extract

7. After adding all of these variables to extract, click on the plus sign with extract and click on the tab "Create Extract"

8. This will take you to a page where you will name and describe the extract. To ensure that this extracted dataset will work with our code for reproducibility reason, please name this dataset "GSS_csv_final"

9. On the second step to "Build Extract", click on the highlighted text "add all variables" and all variables will be added to the extract. After this step, click next

10. On the third step "Choose output options", there are several methods the user can take. For our sanity (as the R Script had difficulty formatting correctly and we did not want to use GSSR to make this project 100% reproducible from scratch), we decided to output this dataset as an excel workbook with data + metadata before exporting the dataset as a .csv file.

In order to do so, first click on the highlighted text "select certain years" and check off only the year 2021. Next, click on excel workbook (data + metadata) and leave metadata fields as label.

11. After all this, click on create extract.

12. When this is done, the excel file will begin to process. Once it is done processing, click on the checkbox beside gss_csv_final.

13. After clicking on the checkbox, click on the actions button and download the excel dataset. This will trigger a download that will save this dataset in a compressed folder.

14. After the download has completed, open the compressed folder with any compression software you'd like. Open the gss_csv_final.tar.gz, then gss_csv_final.tar, then Final, then batch_0tar.gz, then batch_0.tar, then batch_0, then result, then copy files GSS.dat, GSS.xlsx, and post_processing_output into a new folder.

15. Open GSS.xlsx and delete sheets variables and codes.

16. After deleting both, export the xlsx file as a csv file, and save it in our input/data folder as gss_csv_final.csv

17. Voila, the data is now usable by the rest of the programs and will produce the same results that we have made.

### 2023-03-16 outputs/paper/paper3.qmd
Updated quarto doc

@@
 quartoclean5 <- read_csv("../../inputs/data/clean5.csv")
+happycleaned <- read_csv("../../outputs/data/happy_cleaned.csv")
+finaltercleaned <-read_csv("../../outputs/data/finalter_cleaned.csv")
+hapmarcleaned <- read_csv("../../outputs/data/hapmar_cleaned.csv")
+healthcleaned <- read_csv("../../outputs/data/health_cleaned.csv")
+mastercleaned <-read_csv("../../outputs/data/master_cleaned.csv")
 
@@
 ggplot( 
-  quartoclean5, aes(
+  master_clean5, aes(
     x = new_income_range, fill = satfin)) + 
@@
 
+```{r}
+#| label: fig-satfinhappy
+#| fig-cap: ???
+#| echo: false
+
+ggplot( 
+  happycleaned, aes(
+    x = happy, fill = satfin)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Happiness Response", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Financial Satisfaction")
+
+```
+
+```{r}
+#| label: fig-happyincome
+#| fig-cap: ???
+#| echo: false
+
+ggplot( 
+  happycleaned, aes(
+    x = new_income_range, fill = happy)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Happiness Response")
+
+```
+
 # 4 Discussion

### 2023-03-16 scripts/02-data_cleaning.R
made all the graphs, we can still make tables

@@ -108,24 +108,27 @@ rm(master_clean7)
 # we decided to make this subset from master_clean 5
 # because it represents both married, unmarried, or skipped entries respondents.
 master_clean9 <- subset(master_clean5, finalter != ".s:  Skipped on Web")
+master_clean10 <- subset(master_clean9, happy != ".d:  Do not Know/Cannot Choose")
 
 # master_clean 10 will represent the health of all respondents that did not
 # skip the survey question on web. we decided to make this subset from master_clean 5
 # because it represents both married and unmarried respondents.
-master_clean10 <- subset(master_clean5, health != ".s:  Skipped on Web")
+master_clean11 <- subset(master_clean5, health != ".s:  Skipped on Web")
+master_clean12 <- subset(master_clean11, happy != ".d:  Do not Know/Cannot Choose")
 
 # master_clean 11 will represent the happiness of all respondents that did not
 # skip the survey question on web. we decided to make this subset from master_clean 5
 # because it represents both married, unmarried, or skipped entries respondents.
-master_clean11 <- subset(master_clean5, happy != ".s:  Skipped on Web")
+master_clean13 <- subset(master_clean5, happy != ".s:  Skipped on Web")
+master_clean14 <- subset(master_clean13, happy != ".d:  Do not Know/Cannot Choose")
 
 ## Output all of our datasets in usable csvs.
 
 write.csv(master_clean5, "outputs/data/master_cleaned.csv")
 write.csv(master_clean8, "outputs/data/hapmar_cleaned.csv")
-write.csv(master_clean9, "outputs/data/finalter_cleaned.csv")
-write.csv(master_clean10, "outputs/data/health_cleaned.csv")
-write.csv(master_clean11, "outputs/data/happy_cleaned.csv")
+write.csv(master_clean10, "outputs/data/finalter_cleaned.csv")
+write.csv(master_clean12, "outputs/data/health_cleaned.csv")
+write.csv(master_clean14, "outputs/data/happy_cleaned.csv")
 
 
 

### 2023-03-16 outputs/paper/paper3.qmd
Wrote simulation and and added graphs to p3

--- 2023-03-16 outputs/paper/paper3.qmd
@@
 quartoclean5 <- read_csv("../../inputs/data/clean5.csv")
+mastercleaned <-read_csv("../../outputs/data/master_cleaned.csv")
+happycleaned <- read_csv("../../outputs/data/happy_cleaned.csv")
+finaltercleaned <-read_csv("../../outputs/data/finalter_cleaned.csv")
+hapmarcleaned <- read_csv("../../outputs/data/hapmar_cleaned.csv")
+healthcleaned <- read_csv("../../outputs/data/health_cleaned.csv")
 
@@
 
-\newpage
-
 ```{r}
@@
 #| echo: false
-
 ggplot( 
-  quartoclean5, aes(
+  master_clean5, aes(
     x = new_income_range, fill = satfin)) + 
@@
 
+```{r}
+happycleaned %>% 
+  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "cell") %>% 
+  add_p()
+```
+
+```{r}
+#| label: fig-satfinhappy
+#| fig-cap: ???
+#| echo: false
+
+ggplot(
+  happycleaned, aes(
+    x = satfin, fill = happy)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Happiness Response")+
+  scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+
+```
+
+```{r}
+#| label: fig-happyincome
+#| fig-cap: ???
+#| echo: false
+
+ggplot( 
+  happycleaned, aes(
+    x = new_income_range, fill = happy)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Happiness Response")
+
+```
+```{r}
+ggplot( 
+  hapmarcleaned, aes(
+    x = satfin, fill = hapmar)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Happiness of Marriage")+
+  scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+```
+
+```{r}
+#| label: fig-happyincome
+#| fig-cap: ???
+#| echo: false
+
+ggplot( 
+  hapmarcleaned, aes(
+    x = new_income_range, fill = hapmar)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Happiness of Marriage")
+```
+
+```{r}
+ggplot( 
+  healthcleaned, aes(
+    x = new_income_range, fill = health)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Income Ranges", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Health")
+```
+
+```{r}
+ggplot( 
+  healthcleaned, aes(
+    x = satfin, fill = health)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Health")+
+    scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+```
+
+```{r}
+ggplot( 
+  finaltercleaned, aes(
+    x = new_income_range, fill = finalter)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Income Ranges", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Changes in Wealth")
+```
+
+```{r}
+ggplot( 
+  finaltercleaned, aes(
+    x = satfin, fill = finalter)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Changes in Wealth")+
+    scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+```
+
 # 4 Discussion

### 2023-03-16 scripts/00-simulate_data.R

@@ -13,6 +13,49 @@ library(tidyverse)
 # [...UPDATE THIS...]
 
 #### Simulate data ####
-# [...ADD CODE HERE...]
+#Recreate simulated master_clean5 as simulated_clean
 
+#Create list of possible answers in random data (excluding nonresponse answers since they will be omitted in real data)
+happinesses = c("Pretty Happy", "Not too Happy", "Very Happy")
+healths = c("Poor", "Fair", "Good", "Excellent")
+finalters = c("Worse", "Stayed the Same", "Better")
+satfins = c("Not Satisfied at All", "More or less Satisfied", "Pretty well Satisfied")
+income16s = c("UNDER $1 000", "$1 000 TO 2 999", "$3 000 TO 3 999", "$4 000 TO 4 999", "$5 000 TO 5 999", 
+              "$6 000 TO 6 999","$7 000 TO 7 999", "$8 000 TO 9 999","$10000 TO 12499", "$12500 TO 14999", "$15000 TO 17499", "$17500 TO 19999", "$20000 TO 22499", "$22500 TO 24999", "$25000 TO 29999", "$30000 TO 34999", "$35000 TO 39999", "$40000 TO 49999", "$50000 TO 59999", "$60000 TO 74999", "$75000 TO $89999", "$90000 TO $109999", "$110000 TO $129999", "$130000 TO $149999", "$150000 TO $169999", "$170000 OR OVER")
+
+#Create random probabilities of categorical answers for data
+random_happiness = sample(happinesses, 3496, replace = TRUE, prob=c(0.33, 0.33, 0.34))
+random_hapmar = random_happiness
+random_health = sample(healths, 3496, replace = TRUE, prob=c(0.25, 0.25, 0.25, 0.25))
+random_finalters = sample(finalters, 3496, replace = TRUE, prob=c(0.33, 0.33, 0.34))
+random_satfins = sample(satfins, 3496, replace = TRUE, prob=c(0.33, 0.33, 0.34))
+random_income16s = sample(income16s, 3496, replace = TRUE)
+
+#Compose simulated data in a data frame with all variables.
+simulated_clean <- data.frame(random_happiness, random_hapmar, random_health, random_finalters, random_satfins,
+                              random_income16s)
+#Clean simulated data to include new_income_range that will be used later
+simulated_clean$new_income_range <- ifelse(simulated_clean$random_income16s %in% 
+                                             c("UNDER $1 000", "$1 000 TO 2 999", "$3 000 TO 3 999", 
[…]

### 2023-03-16 outputs/paper/paper3.qmd
Added all the necessary tables for analysis

@@
 ```{r}
+master_clean5 %>% 
+  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Financial Satisfaction"), percent = "column")
+```
+```{r}
 happycleaned %>% 
-  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "cell") %>% 
-  add_p()
+  tbl_cross(row = happy, col = satfin, label = list(satfin ~ "Financial Satisfactions", happy ~ "Happiness"), percent = "column")
+```
+```{r}
+happycleaned %>% 
+  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "column")
 ```
@@
 ```{r}
+hapmarcleaned %>% 
+  tbl_cross(row = hapmar, col = satfin, label = list(satfin ~ "Financial Satisfactions", hapmar ~ "Happiness of Marriage"), percent = "column")
+```
+
+```{r}
+hapmarcleaned %>% 
+  tbl_cross(row = hapmar, col = new_income_range, label = list(new_income_range ~ "Income Ranges", hapmar ~ "Happiness of Marriage"), percent = "column")
+```
+
+```{r}
 #| label: fig-happyincome
@@
        fill = "Happiness of Marriage")
+```
+
+```{r}
+healthcleaned %>% 
+  tbl_cross(row = health, col = satfin, label = list(satfin ~ "Financial Satisfactions", health ~ "Quality of Health"), percent = "column")
+```
+
+```{r}
+healthcleaned %>% 
+  tbl_cross(row = health, col = new_income_range, label = list(new_income_range ~ "Income Ranges", health ~ "Quality of Health"), percent = "column")
 ```
@@
     scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+```
+
+```{r}
+finaltercleaned %>% 
+  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
+```
+
+```{r}
+finaltercleaned %>% 
+  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
 ```

### 2023-03-16 scripts/02-data_cleaning.R
cleaning unused files

@@ -12,7 +12,6 @@
 library(tidyverse)
 library(dplyr)
 library(ggplot2)
-# [...UPDATE THIS...]
 
 #### Import the data ####
 GSS <- read_csv("inputs/data/GSS_csv_final.csv")

### 2023-03-16 outputs/paper/paper3.qmd
Graphs and new libraries

--- 2023-03-16 outputs/paper/paper3.qmd
@@
 library(ggplot2)
+library(gtsummary)
+library(flextable)
 
 quartoclean5 <- read_csv("../../inputs/data/clean5.csv")
+mastercleaned <-read_csv("../../outputs/data/master_cleaned.csv")
 happycleaned <- read_csv("../../outputs/data/happy_cleaned.csv")
@@
 healthcleaned <- read_csv("../../outputs/data/health_cleaned.csv")
-mastercleaned <-read_csv("../../outputs/data/master_cleaned.csv")
 
@@
 \newpage
+```{r}
+#| label: table-satfinincome
+#| tbl-cap: Table Visualization of financial satisfaction of respondents with respect to their relative income.
+There is a larger proportion of respondents that claim that they are not satisfied with their finances at lower income ranges.
+As the income range increases, more respondents proportionally express that they are either more of less satisfied, or are pretty well satisfied with their financial situation.
+#| echo: false
+#| message: false
+table_satfinincome <- mastercleaned %>% 
+  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Finances"), percent = "column")
+
+```
 
@@
 #| echo: false
-
 ggplot( 
-  master_clean5, aes(
+  mastercleaned, aes(
     x = new_income_range, fill = satfin)) + 
@@
 
+\newpage
+```{r}
+#| label: table-happyandsatfin
+#| fig-cap: something
+#| echo: false
+#| message: false
+happycleaned %>% 
+  tbl_cross(row = happy, col = satfin, label = list(satfin ~ "Financial Satisfactions", happy ~ "Happiness"), percent = "column")
+```
+```{r}
+#| label: table-happyandincomes
+#| fig-cap: something2
+#| echo: false
+#| message: false
+happycleaned %>% 
+  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "column")
+```
+
+\newpage
+
 ```{r}
 #| label: fig-satfinhappy
-#| fig-cap: ???
+#| fig-cap: something3
 #| echo: false
@@
   happycleaned, aes(
-    x = happy, fill = satfin)) + 
+    x = satfin, fill = happy)) + 
   geom_bar(
@@
     hjust = 1)) + 
-  labs(x = "Happiness Response", #Labeling the axes and fill section
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
        y = "Frequency",
-       fill = "Financial Satisfaction")
+       fill = "Happiness Response")+
+  scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
 
 ```
+\newpage
 
@@
 ```
+\newpage
+```{r}
+#| label: table-hapmarsatfin
+#| fig-cap: something2
+#| echo: false
+#| message: false
+hapmarcleaned %>% 
+  tbl_cross(row = hapmar, col = satfin, label = list(satfin ~ "Financial Satisfactions", hapmar ~ "Happiness of Marriage"), percent = "column")
+```
+
+```{r}
+#| label: table-hapmarincome
+#| fig-cap: something2
+#| echo: false
+#| message: false
+hapmarcleaned %>% 
+  tbl_cross(row = hapmar, col = new_income_range, label = list(new_income_range ~ "Income Ranges", hapmar ~ "Happiness of Marriage"), percent = "column")
+```
+\newpage
+```{r}
+#| label: fig-hapmarsatfin
+#| fig-cap: something2
+#| echo: false
+ggplot( 
+  hapmarcleaned, aes(
+    x = satfin, fill = hapmar)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Happiness of Marriage")+
+  scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+```
+\newpage
+```{r}
+#| label: fig-hapmarincome
+#| fig-cap: ???
+#| echo: false
+
+ggplot( 
+  hapmarcleaned, aes(
+    x = new_income_range, fill = hapmar)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Happiness of Marriage")
+```
+\newpage
+```{r}
+#| label: table-healthsatfin
+#| fig-cap: something2
+#| echo: false
+#| message: false
+healthcleaned %>% 
+  tbl_cross(row = health, col = satfin, label = list(satfin ~ "Financial Satisfactions", health ~ "Quality of Health"), percent = "column")
+```
+
+```{r}
+#| label: table-healthincome
+#| fig-cap: something2
+#| echo: false
+#| message: false
+healthcleaned %>% 
+  tbl_cross(row = health, col = new_income_range, label = list(new_income_range ~ "Income Ranges", health ~ "Quality of Health"), percent = "column")
+```
+\newpage
+```{r}
+#| label: fig-healthsatfin
+#| fig-cap: something2
+#| echo: false
+ggplot( 
+  healthcleaned, aes(
+    x = satfin, fill = health)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Health")+
+    scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+```
+\newpage
+```{r}
+#| label: fig-healthincome
+#| fig-cap: something2
+#| echo: false
+ggplot( 
+  healthcleaned, aes(
+    x = new_income_range, fill = health)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Income Ranges", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Health")
+```
+\newpage
+```{r}
+#| label: table-finaltsatfin
+#| fig-cap: something2
+#| echo: false
+#| message: false
+finaltercleaned %>% 
+  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
+```
+
+```{r}
+#| label: table-finaltincome
+#| fig-cap: something2
+#| echo: false
+#| message: false
+finaltercleaned %>% 
+  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
+```
+\newpage
+```{r}
+#| label: fig-finaltsatfin
+#| fig-cap: something2
+#| echo: false
+ggplot( 
+  finaltercleaned, aes(
+    x = satfin, fill = finalter)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Changes in Wealth")+
+    scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
+```
+\newpage
+```{r}
+#| label: fig-finaltincome
+#| fig-cap: something2
+#| echo: false
+ggplot( 
+  finaltercleaned, aes(
+    x = new_income_range, fill = finalter)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Income Ranges", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Changes in Wealth")
+```
 

### 2023-03-16 scripts/02-data_cleaning.R

@@ -108,13 +108,13 @@ rm(master_clean7)
 # we decided to make this subset from master_clean 5
 # because it represents both married, unmarried, or skipped entries respondents.
 master_clean9 <- subset(master_clean5, finalter != ".s:  Skipped on Web")
-master_clean10 <- subset(master_clean9, happy != ".d:  Do not Know/Cannot Choose")
+master_clean10 <- subset(master_clean9, finalter != ".d:  Do not Know/Cannot Choose")
 
 # master_clean 10 will represent the health of all respondents that did not
 # skip the survey question on web. we decided to make this subset from master_clean 5
 # because it represents both married and unmarried respondents.
 master_clean11 <- subset(master_clean5, health != ".s:  Skipped on Web")
-master_clean12 <- subset(master_clean11, happy != ".d:  Do not Know/Cannot Choose")
+master_clean12 <- subset(master_clean11, health != ".d:  Do not Know/Cannot Choose")
 
 # master_clean 11 will represent the happiness of all respondents that did not
 # skip the survey question on web. we decided to make this subset from master_clean 5

### 2023-03-16 outputs/paper/paper3.qmd
Add changes to and a test table

@@
 table_satfinincome <- mastercleaned %>% 
-  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Finances"), percent = "column")
+  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Finances"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Income Ranges")
+
+table_satfinincome %>%
 

### 2023-03-16 outputs/paper/tabletest.qmd
Add changes to and a test table

--- 2023-03-16 outputs/paper/paper3.qmd
@@
 library(ggplot2)
+library(gtsummary)
+library(flextable)
 
@@
 
+\newpage
 ```{r}
-#| label: fig-satfincome
-#| fig-cap: Visualization of financial satisfaction of respondents with respect to their relative income.
-There is a larger proportion of respondents that claim that they are not satisfied with their finances at lower income ranges.
-As the income range increases, more respondents proportionally express that they are either more of less satisfied, or are pretty well satisfied with their financial situation.
+#| label: table-satfinincome
+#| tbl-cap: Financial Satisfaction vs. Income Ranges
 #| echo: false
-ggplot( 
-  master_clean5, aes(
-    x = new_income_range, fill = satfin)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Income Ranges", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Financial Satisfaction")
+#| message: false
+table_satfinincome <- mastercleaned %>% 
+  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Financial Satisfaction"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Income Ranges")
+
+table_satfinincome %>% autofit() %>% fit_to_width(6.5)
 
 ```
-
-```{r}
-master_clean5 %>% 
-  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Financial Satisfaction"), percent = "column")
-```
-```{r}
-happycleaned %>% 
-  tbl_cross(row = happy, col = satfin, label = list(satfin ~ "Financial Satisfactions", happy ~ "Happiness"), percent = "column")
-```
-```{r}
-happycleaned %>% 
-  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "column")
-```
-
-```{r}
-#| label: fig-satfinhappy
-#| fig-cap: ???
-#| echo: false
-
-ggplot(
-  happycleaned, aes(
-    x = satfin, fill = happy)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Happiness Response")+
-  scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
-
-```
-
-```{r}
-#| label: fig-happyincome
-#| fig-cap: ???
-#| echo: false
-
-ggplot( 
-  happycleaned, aes(
-    x = new_income_range, fill = happy)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Happiness Response")
-
-```
-```{r}
-ggplot( 
-  hapmarcleaned, aes(
-    x = satfin, fill = hapmar)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Happiness of Marriage")+
-  scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
-```
-
-```{r}
-hapmarcleaned %>% 
-  tbl_cross(row = hapmar, col = satfin, label = list(satfin ~ "Financial Satisfactions", hapmar ~ "Happiness of Marriage"), percent = "column")
-```
-
-```{r}
-hapmarcleaned %>% 
-  tbl_cross(row = hapmar, col = new_income_range, label = list(new_income_range ~ "Income Ranges", hapmar ~ "Happiness of Marriage"), percent = "column")
-```
-
-```{r}
-#| label: fig-happyincome
-#| fig-cap: ???
-#| echo: false
-
-ggplot( 
-  hapmarcleaned, aes(
-    x = new_income_range, fill = hapmar)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Happiness of Marriage")
-```
-
-```{r}
-healthcleaned %>% 
-  tbl_cross(row = health, col = satfin, label = list(satfin ~ "Financial Satisfactions", health ~ "Quality of Health"), percent = "column")
-```
-
-```{r}
-healthcleaned %>% 
-  tbl_cross(row = health, col = new_income_range, label = list(new_income_range ~ "Income Ranges", health ~ "Quality of Health"), percent = "column")
-```
-
-```{r}
-ggplot( 
-  healthcleaned, aes(
-    x = new_income_range, fill = health)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Income Ranges", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Health")
-```
-
-```{r}
-ggplot( 
-  healthcleaned, aes(
-    x = satfin, fill = health)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Health")+
-    scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
-```
-
-```{r}
-finaltercleaned %>% 
-  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
-```
-
-```{r}
-finaltercleaned %>% 
-  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
-```
-
-```{r}
-ggplot( 
-  finaltercleaned, aes(
-    x = new_income_range, fill = finalter)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Income Ranges", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Changes in Wealth")
-```
-
-```{r}
-ggplot( 
-  finaltercleaned, aes(
-    x = satfin, fill = finalter)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Financial Satisfaction", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Changes in Wealth")+
-    scale_x_discrete(limit = c("Not satisfied at all", "More or less satisfied", "Pretty well satisfied"))
-```
-
-# 4 Discussion
-
-## 4.1 Limitations
-
-# 5 Appendix

### 2023-03-17 outputs/paper/paper3.qmd
Chris 2 to merge into main

--- 2023-03-16 outputs/paper/paper3.qmd
@@
 # 1 Introduction
-
+##Literature Review
 # 2 Data
+This report focuses on the General Social Survey (GSS), which is a survey that observes and monitors public opinion and behavior in the United States ("US General Social Survey", 2021).
+Since 1972, the GSS has been conducted by the NORC at the University of Chicago, and is currently funded by the National Science Foundation (NSF) This survey was conducted annually until 1990, where it shifted towards a bi-annual schedule.
+Its aim is to maintain a consistent set of questions that aggregates American sentiments through similar sampling and questioning approaches.
+Depending on the year, political context, and contemporary academic practices, additional questions may be added or altered.
+However, there are still a core set of questions that are maintained and given every year.
+These core survey questions are mostly identity related (age, income, gender, etc.), but a few are also relevant to general opinions and well being.
+Additionally, the survey consists of repeating and topical modules, with each participant receiving a subset of both.
+For the scope of this study, we are going to look at survey responses produced from the 2021 survey.
 
@@
 
+This report focuses on the General Social Survey (GSS), which is a survey that observes and monitors public opinion and behavior in the United States ("US General Social Survey", 2021).
+Since 1972, the GSS has been conducted by the NORC at the University of Chicago, and is currently funded by the National Science Foundation (NSF) This survey was conducted annually until 1990, where it shifted towards a bi-annual schedule.
+Its aim is to maintain a consistent set of questions that aggregates American sentiments through similar sampling and questioning approaches.
+Depending on the year, political context, and contemporary academic practices, additional questions may be added or altered.
+However, there are still a core set of questions that are maintained and given every year.
+These core survey questions are mostly identity related (age, income, gender, etc.), but a few are also relevant to general opinions and well being.
+Additionally, the survey consists of repeating and topical modules, with each participant receiving a subset of both.
+For the scope of this study, we are going to look at survey responses produced from the 2021 survey.
+
+The sample for the 2021 survey consisted of adults aged 18 and older living in privately owned homes in the US.
+To select respondents, the "last birthday method" was used, which involves selecting the adult with the most recent birthday to when the mail was sent out.
+Prior to the pandemic, the selection process was more rigorous, with an interviewer physically present to assist respondents and make the selection after all adults had filled in an introductory form.
+For the 2021 survey, materials were mailed to participants with a web link invitation instead.
+The response rate was 17.4%, with 88.3% of respondents completing the survey via the web and 11.7% completing it via phone.
+A total of 4,032 surveys were completed between December 1, 2020, and May 3, 2021.
+
 ## 2.3 Survey Biases and Ethics
+The lack of an interviewer implied the possibility of non-response, as participants are less socially pressured to fill out responses they may or may not feel inclined to report.
+To address this, an introductory form was administered to all participating adults which somewhat ensured that those taking the survey are dedicated enough to offer adequate responses.This was a trade off in the sampling approach that must be noted compared to previous years.
+Therefore, weights were carefully placed to account for factors such as population totals, density of surveyed addresses nearby, and non-response.
+The weighting system must account for new data and be similar to previous years to avoid skewing the results.
+However, despite all of these measures and countermeasures, the greatest challenge against the GSS (in all years) is the threat of survey bias, as all the data collected for all surveys are from participants willing to fill out a 90 minute survey.
+This could mean that the only people represented in the GSS survey are those with the free time and willingness to offer survey responses to NORC, potentially misrepresenting the overall population.
+
+Furthermore, the GSS 2021 survey has made changes to the survey response options due to the shift from in-person interviews to web and phone-based interviews.
+The survey originally contained "volunteered responses" that were not displayed to respondents but used by interviewers.
+However, interviewers are unable to add volunteer responses in this year's survey because of the lack of interaction on web and phone-based interviews.
+The GSS adopted a new structure for volunteered responses on the web mode by creating two different versions of forms, one with and one without volunteered responses as an option.
+Any changes in public opinion seen in the 2021 GSS data could be due to actual changes in public opinion or the newly adopted methodology and should be closely monitored and considered in analysis.
+
+###Nonresponse Bias
+Changes to "Don't Know" and "No Answer" responses have also been made in the 2021 GSS survey.
+Traditionally, these options were not shown to respondents, and it was only recorded if the respondent did not wish to answer.
+On the web mode, however, responders can only skip the question, and the option of "No Answer" was removed.
+The option of "Don't Know" was also removed from attitudinal questions and only displayed in light-gray as an option for factual questions.
+Implementing these changes exposes the survey to more "No Answer" and "Don't Know" responses, which could lead to a loss of information.
+However, the GSS codebook has stated that there was no significant increase in respondents choosing these options, but they encourage further investigation as this finding is still preliminary.
+
+##Survey bias
+The data that was represented in this analysis has many considerations to take into account.
+First, it must be considered that these results are highly generalized, as one respondent in the GSS survey corresponds to 90,000 people.
+This is the result of how the data was collected, and as such the data visualizations are only to be seen in a general context.
+In addition, we also have to consider that opinions of what people are thinking are not substantial enough to confidently argue in absolutes in regards to the correlation between well-being and the variables that were analyzed.
+This also applies to the fact that respondents can still lie on the survey as there is no way to verify if the respondents were answering truthfully over a survey.
+It must also be considered that volunteer bias is present with this survey, as those respondents that have time and access to contribute to the survey would be more likely to take part.
+As a result, this data may misrepresent the population as those that have the free time to offer these opinions may be more well off.
+While it's great to include anyone in the survey, the assumption can be made that more respondents would likely consist of individuals that are well off.
+
+##Sentiment Conceptualization
+Furthermore, the nature of sentiment-based questions in the GSS can be difficult to conceptualize.
+In GSS Methodological Report No.
+127, Tom W.
+Smith investigates the nature of vague questions such as SATJOB (Job Satisfaction) and how it is a subjective concept that varies in definition depending on the respondent.
+Specifically, he quotes another paper that writes "there probably are several types of feelings that people have which can be satisfaction or which influence their feelings of satisfaction about their job."(Wanous and Lawler, 1972) In other words, depending on the categories, feelings, and values respondents assign to their jobs, the satisfaction reported can be wildly different from one.
+
+Similarly, we wish to highlight this limitation in the GSS, as one of our most important variables SATFIN is also a subjective sentiment-based question that we will use to gauge the financial comfort of the respondents.
+To address this limitation, however, we have also decided to include income into our analysis in order to somewhat quantify the varying degrees of financial satisfaction before we set out to measure its impact on various aspects of well being.
+
+Another important vulnerability to identify is the outdatedness of certain variables.
+Specifically, variables such as income(respondent family income) and rincome (respondent income) are not scaled for inflation.
+The 12 income ranges used to represent respondents do not exceed 25 000.
+However, the GSS does acknowledge this, and has implemented different income ranges to accommodate for inflation.
+Specifically, we will be using income16 (respondent family income in 2016 and beyond) to represent the ranges of income of our respondents.
+Furthermore, we will be condensing these ranges during data cleaning to better visually interpret the data.
 
@@
 
+In order to visualize the results of the GSS, the data was extracted from the GSS Data Explorer and was imported and analyzed using R \[\@rcoreteam2022\].
+The tidyverse package \[\@wickham2019\] was used to load in the dplyr package to filter variables \[\@wickham2023\], and ggplot2 to visualize the data in graphs \[\@wickham2016\].
+Furthermore, we also employed packages gtsummary and flextable to create table visualizations and summaries of our findings
+
+The data extraction process requires access to an internet browser, a file compression software such as 7zip, and Microsoft Excel.
+In order to acquire the GSS 2021 data that we have extracted through legal means, please follow the precise steps outlined in our README.md file, in our Github repository.
+
+The data that was chosen to be analyzed from the GSS were variables that involved subjective opinions about the respondent's well-being in tandem with socio-economic variables that act as potential contributors to their state.
+These specific variables are:
+
+-   HAPPY: Subjective opinion of the respondent's happiness
+
+<!-- -->
+
+-   HAPMAR: Subjective opinion of the respondents' current happiness in their marriage (if they are married)
+
+-   HEALTH: Subjective opinion of the respondent's current health status
+
+-   SATFIN: Financial satisfaction of the respondent
+
+-   INCOME16: Total family income of the respondent, which includes: total income includes interest or dividends, rent, social security, other pensions, alimony or child support, unemployment compensation, public aid (welfare), armed forces or veteran's allotment.
+
+-   FINALTER: Subjective opinion of the respondent's financial situation in the past few years since 2021.
+
+Before we chose any of the other variables, we decided to first pick out INCOME16 and SATFIN.
+The reason for this is because we want to be able to gauge what range of income respondents would identify as a range where they would be financially satisfied.
+The reason for this is to quantify financial satisfaction on the basis of income, as this allows us to translate the sentiment of satisfaction into a tangible number.
+Similarly, happiness in a marriage context with HAPMAR was also chosen to be analyzed as social relationships play a large role in a person's sense of belonging, and so we wanted to assess how living with a partner can affect their well-being in a measurable way.
+HEALTH is used to gauge how people feel about their general health condition, and can predict to a certain extent their well-being.
+These variables will be further explored in our data analysis (or can be demonstrated right now in a graph).
+Overall, our attention was turned to three specific factors: finances, relationships, and health.
+These variables were chosen to be analyzed as they represent core dimensions that are interconnected with well-being and how humans experience and feel about life \[\@rath2010\].
+Discussing these factors as they affect your well-being turns them into abstract concepts for people to visualize and describe to others, and so a subjective viewpoint was taken from respondents to gain an idea of how they affect them in a general context.
+
+We also currently have variable "- LIFE: "Subjective opinion of respondent's view on life as dull, routine, or exciting"  included in the data extract.
+We ended up not working with this variable as it only included samples from two out of the 3 ballots employed in 2021.
+
 ## 2.5 Data Cleaning
 
+In order to clean the data, we started by selecting all of the applicable columns to make two separate data frames.
+The first one consisted of SATFIN, which is financial satisfaction, and the INCOME16 column which is a family's yearly income.
+While trying to visualize the data, we decided to make more general income ranges, instead of the twenty six that were provided in the original INCOME16 column.
+We settled on five income ranges (which we will later discuss in discussions).
+We did so by creating an ifelse statement that would add an additional column "new_income_range" with our own set income ranges depending on the INCOME16 value.
+We then removed all invalid entries that consisted of either "incomplete", "did not answer", or "did not complete online" values.
+Similarly, we made another master_clean dataset, in which we selected the columns HAPPY, HAMPAR, HEALTH, FINALTER, SAFTIN, INCOME16, and GROUPED_INC.
+We then followed the same methodology of adding our own column for our custom income range, and removing all invalid entries from all of the invalid rows.
+
 # 3 Results
+
+\newpage
+
+```{r}
+#| label: table-satfinincome
+#| tbl-cap: Financial Satisfaction vs. Income Ranges
+#| echo: false
+#| message: false
+table_satfinincome <- mastercleaned %>% 
+  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Financial Satisfaction"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Income Ranges")
+
+table_satfinincome %>% autofit() %>% fit_to_width(6.5)
+
+```
 
@@
 ggplot( 
-  master_clean5, aes(
-    x = new_income_range, fill = satfin)) + 
+  mastercleaned, aes(
+    x = new_income_range, fill = factor(satfin, levels = c("Pretty well satisfied", "More or less satisfied", "Not satisfied at all")))) + 
   geom_bar(
@@
 
+\newpage
+
 ```{r}
-master_clean5 %>% 
-  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Financial Satisfaction"), percent = "column")
-```
-```{r}
-happycleaned %>% 
-  tbl_cross(row = happy, col = satfin, label = list(satfin ~ "Financial Satisfactions", happy ~ "Happiness"), percent = "column")
-```
-```{r}
-happycleaned %>% 
-  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "column")
+#| label: table-happyandsatfin
+#| fig-cap: something
+#| echo: false
+#| message: false
+table_happinesssatfin <- happycleaned %>% 
+  tbl_cross(row = happy, col = satfin, label = list(satfin ~ "Financial Satisfactions", happy ~ "Happiness"), percent = "column") %>%  as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Happiness")
+
+table_happinesssatfin %>% autofit() %>% fit_to_width(6.5)
 ```
@@
 ```{r}
+#| label: table-happyandincomes
+#| fig-cap: something2
+#| echo: false
+#| message: false
+table_happyandincomes <- happycleaned %>% 
+  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "column") %>%  as_flex_table() %>% set_caption(caption = "Income Ranges vs.
+Happiness")
+
+table_happyandincomes %>% autofit() %>% fit_to_width(6.5)
+```
+
+\newpage
+
+```{r}
 #| label: fig-satfinhappy
-#| fig-cap: ???
+#| fig-cap: something3
 #| echo: false
@@
   happycleaned, aes(
-    x = satfin, fill = happy)) + 
+    x = satfin, fill = factor(happy, levels = c("Very happy", "Pretty happy", "Not too happy")))) + 
   geom_bar(
@@
 
+\newpage
+
 ```{r}
@@
   happycleaned, aes(
-    x = new_income_range, fill = happy)) + 
+    x = new_income_range, fill = factor(happy, levels = c("Very happy", "Pretty happy", "Not too happy")))) + 
   geom_bar(
@@
 ```
+
+\newpage
+
 ```{r}
+#| label: table-satfinincome
+#| tbl-cap: Financial Satisfaction vs. Happiness of Marriage
+#| echo: false
+#| message: false
+table_hapmarsatfin<- hapmarcleaned %>% 
+  tbl_cross(row = hapmar, col = satfin, label = list(satfin ~ "Financial Satisfactions", hapmar ~ "Happiness of Marriage"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Happiness of Marriage")
+
+table_hapmarsatfin %>% autofit() %>% fit_to_width(6.5)
+
+```
+
+```{r}
+#| label: table-hapmarincome
+#| table-cap: Income Range vs. Happiness of Marriage
+#| echo: false
+#| message: false
+table_hapmarincome <- hapmarcleaned %>% 
+  tbl_cross(row = hapmar, col = new_income_range, label = list(new_income_range ~ "Income Ranges", hapmar ~ "Happiness of Marriage"), percent = "column") %>%  as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Happiness of Marriage")
+
+table_hapmarincome %>% autofit() %>% fit_to_width(6.5)
+```
+
+\newpage
+
+```{r}
+#| label: fig-hapmarsatfin
+#| fig-cap: something2
+#| echo: false
 ggplot( 
   hapmarcleaned, aes(
-    x = satfin, fill = hapmar)) + 
+    x = satfin, fill = factor(hapmar, levels = c("VERY HAPPY", "PRETTY HAPPY", "NOT TOO HAPPY")))) + 
   geom_bar(
@@
 
-```{r}
-hapmarcleaned %>% 
-  tbl_cross(row = hapmar, col = satfin, label = list(satfin ~ "Financial Satisfactions", hapmar ~ "Happiness of Marriage"), percent = "column")
-```
+\newpage
 
 ```{r}
-hapmarcleaned %>% 
-  tbl_cross(row = hapmar, col = new_income_range, label = list(new_income_range ~ "Income Ranges", hapmar ~ "Happiness of Marriage"), percent = "column")
-```
-
-```{r}
-#| label: fig-happyincome
+#| label: fig-hapmarincome
 #| fig-cap: ???
@@
   hapmarcleaned, aes(
-    x = new_income_range, fill = hapmar)) + 
+    x = new_income_range, fill = factor(hapmar, levels = c("VERY HAPPY", "PRETTY HAPPY", "NOT TOO HAPPY")))) + 
   geom_bar(
@@
 
+\newpage
+
 ```{r}
-healthcleaned %>% 
-  tbl_cross(row = health, col = satfin, label = list(satfin ~ "Financial Satisfactions", health ~ "Quality of Health"), percent = "column")
+#| label: table-healthsatfin
+#| fig-cap: something2
+#| echo: false
+#| message: false
+table_healthsatfin <- healthcleaned %>% 
+  tbl_cross(row = health, col = satfin, label = list(satfin ~ "Financial Satisfactions", health ~ "Quality of Health"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Health")
+
+table_healthsatfin %>% autofit() %>% fit_to_width(6.5)
 ```
@@
 ```{r}
+#| label: table-healthincome
+#| fig-cap: something2
+#| echo: false
+#| message: false
 healthcleaned %>% 
-  tbl_cross(row = health, col = new_income_range, label = list(new_income_range ~ "Income Ranges", health ~ "Quality of Health"), percent = "column")
+  tbl_cross(row = health, col = new_income_range, label = list(new_income_range ~ "Income Ranges", health ~ "Quality of Health"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Income Ranges vs.
+Health")
+
+table_healthsatfin %>% autofit() %>% fit_to_width(6.5)
 ```
 
+\newpage
+
 ```{r}
+#| label: fig-healthsatfin
+#| fig-cap: something2
+#| echo: false
 ggplot( 
   healthcleaned, aes(
-    x = new_income_range, fill = health)) + 
-  geom_bar(
-    position = "stack") + #Creating a stacked bar plot
-  theme_minimal() + #Using a simple theme
-  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
-    angle = 60, 
-    hjust = 1)) + 
-  labs(x = "Income Ranges", #Labeling the axes and fill section
-       y = "Frequency",
-       fill = "Health")
-```
-
-```{r}
-ggplot( 
-  healthcleaned, aes(
-    x = satfin, fill = health)) + 
+    x = satfin, fill = factor(health, levels = c("Excellent", "Good", "Fair", "Poor")))) + 
   geom_bar(
@@
 
-```{r}
-finaltercleaned %>% 
-  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
-```
+\newpage
 
 ```{r}
-finaltercleaned %>% 
-  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
-```
-
-```{r}
+#| label: fig-healthincome
+#| fig-cap: something2
+#| echo: false
 ggplot( 
-  finaltercleaned, aes(
-    x = new_income_range, fill = finalter)) + 
+  healthcleaned, aes(
+    x = new_income_range, fill = factor(health, levels = c("Excellent", "Good", "Fair", "Poor")))) + 
   geom_bar(
@@
        y = "Frequency",
-       fill = "Changes in Wealth")
+       fill = "Health")
+```
+
+\newpage
+
+```{r}
+#| label: table-finaltsatfin
+#| fig-cap: something2
+#| echo: false
+#| message: false
+finaltercleaned %>% 
+  tbl_cross(row = finalter, col = satfin, label = list(satfin ~ "Financial Satisfaction", finalter ~ "Changes in Wealth"), percent = "column")
 ```
@@
 ```{r}
+#| label: table-finaltincome
+#| fig-cap: something2
+#| echo: false
+#| message: false
+finaltercleaned %>% 
+  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
+```
+
+\newpage
+
+```{r}
+#| label: fig-finaltsatfin
+#| fig-cap: something2
+#| echo: false
 ggplot( 
@@
 
+\newpage
+
+```{r}
+#| label: fig-finaltincome
+#| fig-cap: something2
+#| echo: false
+ggplot( 
+  finaltercleaned, aes(
+    x = new_income_range, fill = finalter)) + 
+  geom_bar(
+    position = "stack") + #Creating a stacked bar plot
+  theme_minimal() + #Using a simple theme
+  theme(axis.text.x=element_text( #Adjusting horizontal axis text to be easily readable
+    angle = 60, 
+    hjust = 1)) + 
+  labs(x = "Income Ranges", #Labeling the axes and fill section
+       y = "Frequency",
+       fill = "Changes in Wealth")
+```
+
 # 4 Discussion

### 2023-03-17 scripts/00-simulate_data.R
Updated test and simulated data scripts to include tests for the simulated dataset

@@ -58,4 +58,3 @@ simulated_clean$new_income_range <- ifelse(simulated_clean$random_income16s %in%
 
 #Quick display of table
 tibble(simulated_clean)
-

### 2023-03-17 scripts/04-test_data.R

@@ -10,6 +10,60 @@
 
 #### Workspace setup ####
 library(tidyverse)
-# [...UPDATE THIS...]
+
 
 #### Test data ####
+
+simulated_clean |> #Test to see if there are only 3496 observations
+  count()
+
+head(simulated_clean) #Test to see the first observations
+tail(simulated_clean) #Test to see the final observations
+
+#HAPPY tests
+
+simulated_clean$random_happiness |> #Testing if happiness is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_happiness |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#HAPMAR tests
+
+simulated_clean$random_hapmar |> #Testing if hapmar is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_hapmar |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#HEALTH tests
+
+simulated_clean$random_health |> #Testing if health is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_health |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#FINALTERS tests
+
+simulated_clean$random_finalters |> #Testing if finalters is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_finalters |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#SATFIN tests
+
+simulated_clean$random_satfins |> #Testing if satfin is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_satfins |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#INCOME16 tests
+
+simulated_clean$new_income_range |> #Testing if income range is defined as a character (qualitative)
+  class()
+
+simulated_clean$new_income_range |> #Test to see if there are 6 unique income ranges from 0 to 170 000 plus others
+  unique()

### 2023-03-17 scripts/04-test_data.R
Updated test data script to include preamble

@@ -1,16 +1,14 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Data: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
-# License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Purpose: Tests for simulated data
+# Author: Justin Abando, Jin Di Liu, Marcin Jaczynski
+# Data: 17 March 2023
+# Contact: justin.abando@mail.utoronto.ca
+# Pre-requisites: Requires data from 00-simulate_data.R to be loaded
+# Any other information needed? N/A
 
 
 #### Workspace setup ####
 library(tidyverse)
-
 
 #### Test data ####
 

### 2023-03-17 outputs/paper/paper3.qmd
Changed the tables, references, and added references

@@
 date-format: "D MMMM YYYY"
-abstract: "DON'T FORGET THIS"
+abstract: "This paper discusses data taken from the 2021 US General Social Survey to analyze the relationship between financial well being and overall individual well being. "
 format: pdf
@@
 # 1 Introduction
-##Literature Review
+
+The advent of 2023 is one marked with economic hardship and depression.
+After the pandemic, markets scrambled as inflation rose to an all time high and signs of economic downturn began creeping through in the form of layoffs and reduced spending.
+Because of this, we wanted to investigate the effects that finances (economic statuses and hardships) have on well being.
+For our investigation, we wished to interrogate elements that we believe are representative of well being in relation to financial wellbeing.
+Specifically, we chose to investigate factors such as happiness, health, happiness of marriage, and life excitement.
+We were able to identify interesting correlations between quality of health, happiness, and happiness of marriage with financial satisfaction and income.
+
+To first get a better grasp of this investigation, we conducted a small literature review on the relationships between finances and well being in the United States.
+A common well known relationship between well being and finances is the positive correlation between Life Satisfaction and Economic well being \[\@helliwell2012world\].
+Furthermore, there are other economic theories that also attempt to interrogate the relationship between happiness and economic well being such as the Easterlin Paradox \[\@easterlin1974does\].
+In this regard, the positive correlation between finances and happiness is well understood.
+However, looking deeper into the literature, we can also identify how the deprivation of economic well being can also negatively impact an individual’s quality of life.
+Specifically, research shows that economic hardship can impact marital quality and cause instability.
+This is due to an increase in occupational and financial stress that generate frustration, stress, anger and depression.
+\[\@conger1990linking\] Furthermore, economic hardships can also inflict long-term consequences on children’s psychological well being in adulthood.
+\[\@sobolewski2005economic\].
+Finally, economic hardships play a major role in increasing depression levels, as depression can emerge as a byproduct of low income, education, being young, and having young children.
+\[\@ross1985hardship\]
+	Based on our brief literature review and the current economic climate of 2023, we were inspired to engage with the GSS 2021 survey data to answer questions about the impact of financial satisfaction with overall well being.
+
 # 2 Data
@@
 
-## 2.1 Tools Used
-
-## 2.2 Survey Methodology
+## 2.1 Survey Methodology
 
@@
 
-## 2.3 Survey Biases and Ethics
+## 2.2 Survey Biases and Ethics
 The lack of an interviewer implied the possibility of non-response, as participants are less socially pressured to fill out responses they may or may not feel inclined to report.
@@
 
-## 2.4 Data Collection
+## 2.3 Data Collection
 
@@
 The tidyverse package \[\@wickham2019\] was used to load in the dplyr package to filter variables \[\@wickham2023\], and ggplot2 to visualize the data in graphs \[\@wickham2016\].
-Furthermore, we also employed packages gtsummary and flextable to create table visualizations and summaries of our findings
+Furthermore, we also employed packages gtsummary \[\@gtsummary\] and \[\@flextable\]  to create table visualizations and summaries of our findings
 
@@
 
-## 2.5 Data Cleaning
+## 2.4 Data Cleaning
 

### 2023-03-17 outputs/paper/paper3.qmd
Updated .qmd to include updated headers and abstract

--- 2023-03-16 outputs/paper/paper3.qmd
@@
 date-format: "D MMMM YYYY"
-abstract: "DON'T FORGET THIS"
+abstract: "This paper discusses data taken from the 2021 US General Social Survey to analyze the relationship between finances and overall individual well being.
+Specifically, this paper looks to analyze and determine the relationships between financial well being and factors such as happiness, health, and marriage quality.
+The analysis provided a positive relationship between the two, however many confounding limitations still exist in regards to the possible interpretations of the data.
+Another survey is included at the end designed with the intention to better understand these variables with less limitation."
 format: pdf
@@
 
-# 1 Introduction
+# 1 Introduction {sec-introduction}
 
-# 2 Data
+# 2 Data {sec-data}
 
-## 2.1 Tools Used
+## 2.1 Tools Used {sec-toolsused}
 
-## 2.2 Survey Methodology
+## 2.2 Survey Methodology {sec-surveymethods}
 
-## 2.3 Survey Biases and Ethics
+## 2.3 Survey Biases and Ethics {sec-surveyethics}
 
-## 2.4 Data Collection
+## 2.4 Data Collection {sec-datacollection}
 
-## 2.5 Data Cleaning
+## 2.5 Data Cleaning {sec-datacleaning}
 
-# 3 Results
+# 3 Results {sec-results}
 
 \newpage
+
 ```{r}
@@
 \newpage
+
 ```{r}
@@
 ```
+
 \newpage
@@
 ```
+
 \newpage
+
 ```{r}
@@
 
-# 4 Discussion
+# 4 Discussion {sec-discussion}
 
-## 4.1 Limitations
+## 4.1 Limitations {sec-limitations}
 
-# 5 Appendix
+# 5 Appendix {sec-appendix}

### 2023-03-17 outputs/paper/paper3.qmd
Updated .qmd with data cleaning methodologies

@@
 
+This process requires access to an internet browser, a file compression software such as 7zip, and Microsoft Excel.
+In order to acquire the GSS 2021 data that we have extracted through legal means, please follow the precise steps outlined in our README.md file in our Github repository.
+
+In order to visualize the results of the GSS, the data was imported and analyzed using R [@rcoreteam2022].
+The tidyverse package [@wickham2019] was used to load in the dplyr package to filter variables [@wickham2023], and ggplot2 to visualize the data in graphs [@wickham2016].
+
+The data that was chosen to be analyzed from the GSS were variables that involved subjective opinions about the respondent’s well-being in tandem with socioeconomic variables that act as potential contributors to their state.
+These specific variables are:
+
+HAPPY: Subjective opinion of the respondent’s happiness
+HAPMAR: Subjective opinion of the respondents’ current happiness in their marriage (if they are married)
+HEALTH: Subjective opinion of the respondent’s current health status
+SATFIN: Financial satisfaction of the respondent
+INCOME16: Total family income of the respondent, which includes: total income includes interest or dividends, rent, social security, other pensions, alimony or child support, unemployment compensation, public aid (welfare), armed forces or veteran's allotment.
+FINALTER: Subjective opinion of the respondent’s financial situation in the past few years since 2021.
+
+Before we chose any of the other variables, we decided to first pick out INCOME16 and SATFIN.
+The reason for this is because we want to be able to gauge what range of income respondents would identify as a range where they would be financially satisfied.
+The reason for this is to quantify financial satisfaction on the basis of income, as this allows us to translate the sentiment of satisfaction into a tangible number.
+Similarly, happiness in a marriage context with HAPMAR was also chosen to be analyzed as social relationships play a large role in a person’s sense of belonging, and so we wanted to assess how living with a partner can affect their well-being in a measurable way.
+HEALTH is used to gauge how people feel about their general health condition, and can predict to a certain extent their well-being.
+These variables will be further explored in our data analysis (or can be demonstrated right now in a graph).
+Overall, our attention was turned to three specific factors: finances, relationships, and health.
+These variables were chosen to be analyzed as they represent core dimensions that are interconnected with well-being and how humans experience and feel about life [@rath2010].
+Discussing these factors as they affect your well-being turns them into abstract concepts for people to visualize and describe to others, and so a subjective viewpoint was taken from respondents to gain an idea of how they affect them in a general context.
+
 ## 2.5 Data Cleaning {sec-datacleaning}
 
+In order to clean the data, we started by selecting all of the applicable columns to make two separate data frames.
+The first one consisted of SATFIN, which is financial satisfaction, and the INCOME16 column which is a family’s yearly income.
+While trying to visualize the data, we decided to make more general income ranges, instead of the twenty six that were provided in the original INCOME16 column.
+We settled on five income ranges.
+We did so, by creating an ifelse statement that would add an additional column “new_income_range” with our own set income ranges depending on the INCOME16 value.
+We then removed all invalid entries that consisted of either “incomplete”, “did not answer”, or “did not complete online” values.
+Similarly, we made another master_clean dataset, in which we selected the columns HAPPY, HAMPAR, HEALTH, FINALTER, SAFTIN, INCOME16, and GROUPED_INC.
+We then followed the same methodology of adding our own column for our custom income range, and removing all invalid entries from all of the invalid rows.
+
 # 3 Results {sec-results}
+
+In this section we cross-analyze each of the variables as outlined in {sec-datacollection} with themselves.
+This involves comparing the answers from two questions on the survey in order to draw potential trends between the respondents' feelings about the specific topic and their opinion of their well-being in relation to it.
 

### 2023-03-17 outputs/paper/paper3.qmd
Fixed some stuff and added stuff

--- 2023-03-17 outputs/paper/paper3.qmd
@@
 ---
-title: "Well-being of Individuals from the United States Global Social Survey are Affected by Finances, Relationships, and Health"
+title: "Finances and Individual Well Being"
 author: "Justin Abando, Jin Di Liu, Marcin Jaczynski"
@@
 date-format: "D MMMM YYYY"
-abstract: "This paper discusses data taken from the 2021 US General Social Survey to analyze the relationship between financial well being and overall individual well being. "
+abstract: "This paper discusses data taken from the 2021 US General Social Survey to analyze the relationship between finances and overall individual well being.
+Specifically, this paper looks to analyze and determine the relationships between financial well being and factors such as happiness, health, and marriage quality.
+The analysis provided a positive relationship between the two, however many confounding limitations still exist in regards to the possible interpretations of the data.
+Another survey is included at the end designed with the intention to better understand these variables with less limitation."
 format: pdf
@@
 To first get a better grasp of this investigation, we conducted a small literature review on the relationships between finances and well being in the United States.
-A common well known relationship between well being and finances is the positive correlation between Life Satisfaction and Economic well being \[\@helliwell2012world\].
-Furthermore, there are other economic theories that also attempt to interrogate the relationship between happiness and economic well being such as the Easterlin Paradox \[\@easterlin1974does\].
+A common well known relationship between well being and finances is the positive correlation between Life Satisfaction and Economic well being [@helliwell2012world].
+Furthermore, there are other economic theories that also attempt to interrogate the relationship between happiness and economic well being such as the Easterlin Paradox [@easterlin1974does].
 In this regard, the positive correlation between finances and happiness is well understood.
@@
 This is due to an increase in occupational and financial stress that generate frustration, stress, anger and depression.
-\[\@conger1990linking\] Furthermore, economic hardships can also inflict long-term consequences on children’s psychological well being in adulthood.
-\[\@sobolewski2005economic\].
+[@conger1990linking] Furthermore, economic hardships can also inflict long-term consequences on children psychological well being in adulthood.
+[@sobolewski2005economic].
 Finally, economic hardships play a major role in increasing depression levels, as depression can emerge as a byproduct of low income, education, being young, and having young children.
-\[\@ross1985hardship\]
+[@ross1985hardship]
 	Based on our brief literature review and the current economic climate of 2023, we were inspired to engage with the GSS 2021 survey data to answer questions about the impact of financial satisfaction with overall well being.
@@
 
-###Nonresponse Bias
 Changes to "Don't Know" and "No Answer" responses have also been made in the 2021 GSS survey.
@@
 
-##Survey bias
 The data that was represented in this analysis has many considerations to take into account.
@@
 
-##Sentiment Conceptualization
 Furthermore, the nature of sentiment-based questions in the GSS can be difficult to conceptualize.
@@
 
-In order to visualize the results of the GSS, the data was extracted from the GSS Data Explorer and was imported and analyzed using R \[\@rcoreteam2022\].
-The tidyverse package \[\@wickham2019\] was used to load in the dplyr package to filter variables \[\@wickham2023\], and ggplot2 to visualize the data in graphs \[\@wickham2016\].
-Furthermore, we also employed packages gtsummary \[\@gtsummary\] and \[\@flextable\]  to create table visualizations and summaries of our findings
+In order to visualize the results of the GSS, the data was extracted from the GSS Data Explorer and was imported and analyzed using R [@rcoreteam2022].
+The tidyverse package [@wickham2019] was used to load in the dplyr package to filter variables [@wickham2023], and ggplot2 to visualize the data in graphs [@wickham2016].
+Furthermore, we also employed packages gtsummary [@gtsummary] and [@flextable]  to create table visualizations and summaries of our findings
 
@@
 #| label: table-happyandsatfin
-#| fig-cap: something
+#| tbl-cap: Financial Satisfaction vs. Happiness
 #| echo: false
@@
 #| label: table-happyandincomes
-#| fig-cap: something2
+#| tbl-cap: Income Ranges vs. Happiness
 #| echo: false
@@
 ```{r}
-#| label: table-satfinincome
+#| label: table-hapmarsatfin
 #| tbl-cap: Financial Satisfaction vs. Happiness of Marriage
@@
 #| label: table-hapmarincome
-#| table-cap: Income Range vs. Happiness of Marriage
+#| tbl-cap: Income Range vs. Happiness of Marriage
 #| echo: false
@@
 #| label: table-healthsatfin
-#| fig-cap: something2
+#| tbl-cap: Financial Satisfaction vs. Health
 #| echo: false
@@
 #| label: table-healthincome
-#| fig-cap: something2
+#| tbl-cap: Income Ranges vs. Health
 #| echo: false
 #| message: false
-healthcleaned %>% 
+table_healthcleaned <- healthcleaned %>% 
   tbl_cross(row = health, col = new_income_range, label = list(new_income_range ~ "Income Ranges", health ~ "Quality of Health"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Income Ranges vs.
@@
 
-table_healthsatfin %>% autofit() %>% fit_to_width(6.5)
+table_healthcleaned %>% autofit() %>% fit_to_width(6.5)
 ```
@@
 #| label: table-finaltsatfin
-#| fig-cap: something2
+#| tbl-cap: Financial Satisfaction vs. Changes in Finances
 #| echo: false
 #| message: false
-finaltercleaned %>% 
-  tbl_cross(row = finalter, col = satfin, label = list(satfin ~ "Financial Satisfaction", finalter ~ "Changes in Wealth"), percent = "column")
+table_altsat<- finaltercleaned %>% 
+  tbl_cross(row = finalter, col = satfin, label = list(satfin ~ "Financial Satisfaction", finalter ~ "Changes in Wealth"), percent = "column") %>% as_flex_table() %>% set_caption(caption = "Financial Satisfaction vs.
+Changes in Finances")
+
+table_altsat %>% autofit() %>% fit_to_width(6.5)
 ```
@@
 #| label: table-finaltincome
-#| fig-cap: something2
+#| tbl-cap: Income Ranges vs. Changes in Finances
 #| echo: false
 #| message: false
-finaltercleaned %>% 
-  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
+table_altinc<- finaltercleaned %>% 
+  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")%>% as_flex_table() %>% set_caption(caption = "Income Ranges vs.
+Changes in Finances")
+
+table_altinc %>% autofit() %>% fit_to_width(6.5)
 ```

### 2023-03-17 outputs/paper/paper3.qmd
Everything you can see

@@
 
+\newpage
+
 # 3 Results
-
-\newpage
 
@@
 
+According to [graph0], when comparing the financial satisfaction of respondents with their income ranges, the number of respondents from the $0 - $89,999 ranges that claim they are not satisfied at all are relatively similar.
+However, when examining the total number of respondents within their respective income ranges, it can be seen that it increases as the income range increases.
+This indicates that the proportion of respondents that do not feel satisfied at all decreases as the income range increases.
+Conversely, more respondents claim that they are either more or less satisfied or pretty well satisfied as the income range increases, and are heavily skewed to those that have higher income ranges.
+
 \newpage
@@
 #| label: fig-satfinhappy
-#| fig-cap: something3
+#| fig-cap: Relation between financial satisfaction and general happiness.
+More respondents appear to demonstrate they are generally happier when they also feel that they are financially satisfied.
+Conversely, a higher proportion of respondents that say that they are not financially satisfied are also not too happy as well, indicating a link between their general happiness with financial satisfaction.
 #| echo: false
@@
 
+The comparison between the respondents’ happiness and financial satisfaction are visualized on [graph].
+We observe that the number of respondents that claimed that they are generally happy increased as the financial satisfaction of these respondents increased as well.
+A higher proportion of respondents that claim they are not too happy also respond that they are not financially satisfied, and so there seems to be a pattern of general happiness being linked to financial satisfaction.
+
 \newpage
@@
 #| label: fig-happyincome
-#| fig-cap: ???
+#| fig-cap: Relation between combined family income and general happiness of respondents.
+The happiness response proportions are relatively similar throughout each income range, with most respondents claiming they are pretty happy, and very happy responses increasing as the income range also increases.
 #| echo: false
@@
 ```
+
+The observation of respondents that describe their level of happiness compared to their income is demonstrated on [graph].
+Each income group shows relatively similar proportions of respondents that claim that they are pretty happy, with fewer proportions claiming they are not too happy or very happy.
+However, as the income range increases, more respondents claim that they are pretty happy or very happy.
+There is an interesting observation with those families with a combined income of $40,000 to $89,999.
+This income group seems to have a slightly disproportionate amount of respondents saying they are not too happy when comparing with the proportions of other income groups.
 
@@
 #| label: fig-hapmarsatfin
-#| fig-cap: something2
+#| fig-cap: Relation between married respondents’ opinion on their marriage and financial satisfaction.
+Respondents that claim they are happy in their marriage also express that they are financially satisfied.
+For respondents that claimed they are not satisfied financially, there are proportionally more respondents that also express they are not too happy within their marriage.
 #| echo: false
@@
 
+For those that are married, a visualization of their financial satisfaction compared to their view of happiness in their marriage is seen in [graph].
+It can be seen that most respondents that are more or less satisfied financially or pretty well satisfied generally are either pretty happy or very happy with their marriage.
+This also applies to respondents that claim they are not satisfied at all financially, however there is a lower frequency of respondents in this category.
+As a result, there is a higher proportion of respondents that claim that they are not too happy in their marriage in comparison to those respondents that claim they are more or less satisfied or pretty satisfied financially.
 \newpage
@@
 #| label: fig-hapmarincome
-#| fig-cap: ???
+#| fig-cap: Relation between married respondents’ opinion on their marriage and combined family income.
+As the combined family income increases, higher proportions of respondents claim that they are pretty happy or very happy with their marriage.
 #| echo: false
@@
 ```
+
+From observing [Graph 2.2] the amount of respondents that are not too happy with their marriage are in the income range of 40,000 to 90,000.
+The number of not too happy responses is seen to increase as does income, however it falls slightly in the income range of 90,000 to 170,000 from the previous group.
+Additionally, very happy marriages are seen to be steadily increasing along with the income.
 
@@
 #| label: fig-healthsatfin
-#| fig-cap: something2
+#| fig-cap: Relation between married respondents’ opinion on their marriage and financial satisfaction. 
 #| echo: false
@@
 
+According to the [Graph 3.1] all three of the financial satisfaction groups have a proportional good health.
+However, those who are not satisfied at all have the lowest number of excellent health, those who are more or less satisfied contain the second highest amount of excellent health and those who are pretty well satisfied have the highest amount of excellent health.
+Additionally, poor health is seen to be decreasing as satisfaction increases, with it being almost not present in the pretty well satisfied group.
+
 \newpage
@@
 #| label: fig-healthincome
-#| fig-cap: something2
+#| fig-cap: Relation between health and family income of respondents.
+With an increase of income the claim of excellent health increases.
+In the ranges of 40 000 and below poor health is more apparent.
 #| echo: false
@@
 ```
+From observing [graph 3.2] as income increases so does the number of excellent health responses.
+The three income ranges that fit into the category of below 40,00 all have a relatively low amount of excellent health responses, and a moderate amount of good and fair health.
+However, from the income ranges that include 40,000 and more, the excellent health response is much larger, meanwhile good health occupies the majority of responses.
+Additionally, as income increases the poor health responses is also seen to slightly decrease.
 
@@
 #| label: fig-finaltsatfin
-#| fig-cap: something2
+#| fig-cap: Relation between wealth changes and financial satisfaction of respondents. As changes in wealth have gotten better the more likely the respondents are to be financially satisfied. 
 #| echo: false
@@
 ```
-
+While looking at the [graph 5.1],  we have observed respondents that are pretty well satisfied with their financial situation that claim that their changes in wealth have gotten better, and almost none that are satisfied claim that their wealth has gotten worse.
+Additionally, more than half of those not satisfied with their financial situation claim that their financial situations have gotten worse over time, and only less than a minority are not satisfied at all as their changes in wealth have gotten better.
+The majority of the respondents that claim that they are more or less satisfied with their finances claim that their changes in wealth have either gotten better or stayed the same, and only a minority believes that they have gotten worse.
+Ultimately those that have either experienced a better or the same change in wealth are more likely to be either more or less satisfied or pretty well satisfied.
+Meanwhile, whore who have experienced a worse change of wealth have become less satisfied.
 \newpage
@@
 #| label: fig-finaltincome
-#| fig-cap: something2
+#| fig-cap: Relation between wealth changes and family income of respondents.
+As income increases so does the belief that the financial situation has gotten better.
+Additionally those making 40 000 or less mostly believe their financial wealth has remained the same or gotten worse.
 #| echo: false
@@
 ```
+According to [graph 4.2], the majority of respondents who claim that their changes in wealth have gotten better, fall into the 40,000 to 89,999 as well as the 90,000 to 170,000 income ranges.
+Additionally, a good portion of the respondents in the following two income ranges, claim that their wealth has remained the same, and only a minority believes that their wealth has gotten worse.
+On the other end of the graph, the income groups ranging from 0 to 9,999 , 10,000 to 19,999 and 20,000 to 39,000 are all almost fairly equally split between believing that their wealth changes are either better, the same, or worse.
 
@@
 
-## 4.1 Limitations
+## 4.1 Income Ranges and Financial Satisfaction
+
+	Our initial decision to investigate income ranges with financial satisfaction is an attempt to quantify financial well being.
+In both the table and graph, we are able to identify what ranges of income do financially satisfied individuals identify with.
+Specifically, we can see the overall trend that those that are well/more or less satisfied fall under higher income ranges while those who are not fall under lower income ranges.
+
+	One major limitation of this and our results is the unfortunate decision to segregate incomes ranges by such large margins.
+The decision to represent income groups below the American Poverty Line with multiple bars while representing wealthier groups with only 2 makes it difficult to determine at what point does strong financial backgrounds start to improve well being.
+Nevertheless, this specific decision also allows us to interpret the degrees of financial hardship that can impact health and happiness.
+
+## 4.2 Happiness, Health, and Changes in Wealth
+
+	As demonstrated by our graphical representations, respondents who rated themselves higher in financial satisfaction and earned more income often rated themselves higher in happiness, health, and marriage quality.
+This reinforces the literature that we have read before, as both happiness and health are to some extent influenced by these variables.
+As demonstrated in the tables for health, respondents who are very satisfied with their finances or earn more than 90 000 proportionately overrepresent those who possess an excellent quality of health.
+Similarly, individuals who are financially satisfied overrepresent the proportion of those who are considered very happy.
+
+	One aspect we did not take into account is age.
+We believed that especially for financial satisfaction, age can be an incredibly important factor as older individuals may feel financially satisfied earning less income from many years of growing their individual assets.
+This means the impact and financial satisfaction can have on happiness and health can be skewed by the pre-existing wealth of respondents.
+	The relationship between financial satisfaction and changes in income is very interesting.
+While changes in wealth and income indicated an even proportion of individuals that had incomes that improved, stayed the same, or gotten better, respondents that experienced worse changes in wealth over-represent those who are not satisfied with their financial situations.
+This bias is interesting, as it demonstrates the sentiment-based nature of the variable of financial satisfaction.
+In this regard, a more accurate survey to probe financial well-being should be targeted towards one’s financial ability to make ends meet.
+
+## 4.3 Survey Biases
+
+As mentioned earlier in the paper, the GSS randomly selects participants by randomly choosing households across the United States.
+This random sampling is further randomized by the quasi-random last birthday sampling method, where each household provides one respondent who most recently just had their birthday.
+
+While these are excellent random sampling practices, the GSS website also writes that the way this data should be interpreted is that each respondent is representative of 90 000 other individuals.
+In this regard, survey bias is still an extremely strong deterrent against the data being truly representative of the whole United States population.
+As written earlier in section data bias, consent requires that those who participate in the GSS possess the necessary free time to perform a 90 minute long survey.
+
+This can impact the quality of this survey in multiple ways.
+Especially for one concerned with financial well being, those struggling to make ends meet may feel less incentivized to take this survey, thereby limiting their representation.
+This is possibly evident in the income distribution of respondents, as there is an overrepresentation of those in the middling income ranges between 40 000 to 170 000 over while very little beneath.
+
+## 4.4 Conclusion
+
+	Based on the discussion, analysis, and limitations of the data, we found that the GSS provides excellent insight in representing the relationship between finances and overall well being.
+However, the sentimentally-based nature of some questions and difficulty to represent financial well being makes it difficult to answer our original question.
+Hence, in the appendix, we have composed a survey that we believe can compose a data-set capable of answering our question.
+We included questions that specify financial well being by specifying financial comfort and ability to hold down emergency payments.
+Furthermore, other factors such as stress, hope, and other feelings are included to better represent the psychological factors of overall well being.
 

### 2023-03-17 outputs/paper/paper3.qmd
Updated .qmd with figure captions and data section

@@
 
-According to [graph0], when comparing the financial satisfaction of respondents with their income ranges, the number of respondents from the $0 - $89,999 ranges that claim they are not satisfied at all are relatively similar.
+According to @fig-satfincome, when comparing the financial satisfaction of respondents with their income ranges, the number of respondents from the $0 - $89,999 ranges that claim they are not satisfied at all are relatively similar.
 However, when examining the total number of respondents within their respective income ranges, it can be seen that it increases as the income range increases.
@@
 
-The comparison between the respondents’ happiness and financial satisfaction are visualized on [graph].
+The comparison between the respondents’ happiness and financial satisfaction are visualized on @fig-satfinhappy.
 We observe that the number of respondents that claimed that they are generally happy increased as the financial satisfaction of these respondents increased as well.
@@
 
-The observation of respondents that describe their level of happiness compared to their income is demonstrated on [graph].
+The observation of respondents that describe their level of happiness compared to their income is demonstrated on @fig-happyincome.
 Each income group shows relatively similar proportions of respondents that claim that they are pretty happy, with fewer proportions claiming they are not too happy or very happy.
@@
 
-For those that are married, a visualization of their financial satisfaction compared to their view of happiness in their marriage is seen in [graph].
+For those that are married, a visualization of their financial satisfaction compared to their view of happiness in their marriage is seen in @fig-hapmarsatfin.
 It can be seen that most respondents that are more or less satisfied financially or pretty well satisfied generally are either pretty happy or very happy with their marriage.
@@
 As a result, there is a higher proportion of respondents that claim that they are not too happy in their marriage in comparison to those respondents that claim they are more or less satisfied or pretty satisfied financially.
+
 \newpage
@@
 
-From observing [Graph 2.2] the amount of respondents that are not too happy with their marriage are in the income range of 40,000 to 90,000.
-The number of not too happy responses is seen to increase as does income, however it falls slightly in the income range of 90,000 to 170,000 from the previous group.
+From observing @fig-hapmarincome, the amount of respondents that are not too happy with their marriage are in the income range of 40,000 to 90,000.
+The number of not too happy responses is seen to increase as does income, however it falls slightly in the income range of $90,000 to $170,000 from the previous group.
 Additionally, very happy marriages are seen to be steadily increasing along with the income.
@@
 #| fig-cap: Relation between married respondents’ opinion on their marriage and financial satisfaction.
+As respondents claim that they are pretty well financially satisfied, their perceived health is also viewed with fewer poor responses, as well as a higher proportion of respondents claiming that their health status is either good, fair, and excellent.
 #| echo: false
@@
 
-According to the [Graph 3.1] all three of the financial satisfaction groups have a proportional good health.
+According to the @fig-healthsatfin all three of the financial satisfaction groups have a proportional good health.
 However, those who are not satisfied at all have the lowest number of excellent health, those who are more or less satisfied contain the second highest amount of excellent health and those who are pretty well satisfied have the highest amount of excellent health.
@@
 With an increase of income the claim of excellent health increases.
-In the ranges of 40 000 and below poor health is more apparent.
+In the ranges of $40,000 and below, claims that respondents exhibit poor health is more apparent.
+Conversely, those respondents in the $90,000 range and above claim they have excellent health.
 #| echo: false
@@
 ```
-From observing [graph 3.2] as income increases so does the number of excellent health responses.
-The three income ranges that fit into the category of below 40,00 all have a relatively low amount of excellent health responses, and a moderate amount of good and fair health.
-However, from the income ranges that include 40,000 and more, the excellent health response is much larger, meanwhile good health occupies the majority of responses.
-Additionally, as income increases the poor health responses is also seen to slightly decrease.
+
+From observing @fig-healthincome as income increases so does the number of excellent health responses.
+The three income ranges that fit into the category of below $40,000 all have a relatively low amount of excellent health responses, and a moderate amount of good and fair health.
+However, from the income ranges that include $40,000 and more, the excellent health response is much larger, meanwhile good health occupies the majority of responses.
+Additionally, as income increases the poor health responses are also seen to slightly decrease.
 
@@
 #| label: fig-finaltsatfin
-#| fig-cap: Relation between wealth changes and financial satisfaction of respondents. As changes in wealth have gotten better the more likely the respondents are to be financially satisfied. 
+#| fig-cap: Relation between wealth changes and financial satisfaction of respondents.
+As their opinion on their changes in wealth are more positive, the more likely the respondents claim to be financially satisfied.
+Conversely, those that feel they are not financially satisfied claim that their changes in health have been generally worse in recent times.
 #| echo: false
@@
 ```
-While looking at the [graph 5.1],  we have observed respondents that are pretty well satisfied with their financial situation that claim that their changes in wealth have gotten better, and almost none that are satisfied claim that their wealth has gotten worse.
+
+While looking at the @fig-finaltsatfin, we have observed respondents that are pretty well satisfied with their financial situation that claim that their changes in wealth have gotten better, and almost none that are satisfied claim that their wealth has gotten worse.
 Additionally, more than half of those not satisfied with their financial situation claim that their financial situations have gotten worse over time, and only less than a minority are not satisfied at all as their changes in wealth have gotten better.
@@
 As income increases so does the belief that the financial situation has gotten better.
-Additionally those making 40 000 or less mostly believe their financial wealth has remained the same or gotten worse.
+Additionally those making $40,000 or less mostly believe their financial wealth has remained the same or gotten worse.
 #| echo: false
@@
 ```
-According to [graph 4.2], the majority of respondents who claim that their changes in wealth have gotten better, fall into the 40,000 to 89,999 as well as the 90,000 to 170,000 income ranges.
+
+According to @fig-finatincome, the majority of respondents who claim that their changes in wealth have gotten better, fall into the $40,000 to $89,999 as well as the $90,000 to $170,000 income ranges.
 Additionally, a good portion of the respondents in the following two income ranges, claim that their wealth has remained the same, and only a minority believes that their wealth has gotten worse.
-On the other end of the graph, the income groups ranging from 0 to 9,999 , 10,000 to 19,999 and 20,000 to 39,000 are all almost fairly equally split between believing that their wealth changes are either better, the same, or worse.
+On the other end of the graph, the income groups ranging from $0 to $9,999, $10,000 to $19,999 and $20,000 to $39,000 are all almost fairly equally split between believing that their wealth changes are either better, the same, or worse.
 
@@
 This means the impact and financial satisfaction can have on happiness and health can be skewed by the pre-existing wealth of respondents.
+
 The relationship between financial satisfaction and changes in income is very interesting.

### 2023-03-17 outputs/paper/paper3.qmd
final copy

@@
 In this regard, the positive correlation between finances and happiness is well understood.
-However, looking deeper into the literature, we can also identify how the deprivation of economic well being can also negatively impact an individual’s quality of life.
+However, looking deeper into the literature, we can also identify how the deprivation of economic well being can also negatively impact an individual's quality of life.
 Specifically, research shows that economic hardship can impact marital quality and cause instability.
@@
 Finally, economic hardships play a major role in increasing depression levels, as depression can emerge as a byproduct of low income, education, being young, and having young children.
-[@ross1985hardship]
-	Based on our brief literature review and the current economic climate of 2023, we were inspired to engage with the GSS 2021 survey data to answer questions about the impact of financial satisfaction with overall well being.
+[@ross1985hardship] Based on our brief literature review and the current economic climate of 2023, we were inspired to engage with the GSS 2021 survey data to answer questions about the impact of financial satisfaction with overall well being.
 
 # 2 Data
+
 This report focuses on the General Social Survey (GSS), which is a survey that observes and monitors public opinion and behavior in the United States ("US General Social Survey", 2021).
@@
 ## 2.2 Survey Biases and Ethics
+
 The lack of an interviewer implied the possibility of non-response, as participants are less socially pressured to fill out responses they may or may not feel inclined to report.
@@
 
-We also currently have variable "- LIFE: "Subjective opinion of respondent's view on life as dull, routine, or exciting"  included in the data extract.
+We also currently have variable "- LIFE:"Subjective opinion of respondent's view on life as dull, routine, or exciting" included in the data extract.
 We ended up not working with this variable as it only included samples from two out of the 3 ballots employed in 2021.
@@
 
-According to @fig-satfincome, when comparing the financial satisfaction of respondents with their income ranges, the number of respondents from the $0 - $89,999 ranges that claim they are not satisfied at all are relatively similar.
+According to @fig-satfincome, when comparing the financial satisfaction of respondents with their income ranges, the number of respondents from the \$0 - \$89,999 ranges that claim they are not satisfied at all are relatively similar.
 However, when examining the total number of respondents within their respective income ranges, it can be seen that it increases as the income range increases.
@@
 
-The comparison between the respondents’ happiness and financial satisfaction are visualized on @fig-satfinhappy.
+The comparison between the respondents' happiness and financial satisfaction are visualized on @fig-satfinhappy.
 We observe that the number of respondents that claimed that they are generally happy increased as the financial satisfaction of these respondents increased as well.
@@
 However, as the income range increases, more respondents claim that they are pretty happy or very happy.
-There is an interesting observation with those families with a combined income of $40,000 to $89,999.
+There is an interesting observation with those families with a combined income of \$40,000 to \$89,999.
 This income group seems to have a slightly disproportionate amount of respondents saying they are not too happy when comparing with the proportions of other income groups.
@@
 From observing @fig-hapmarincome, the amount of respondents that are not too happy with their marriage are in the income range of 40,000 to 90,000.
-The number of not too happy responses is seen to increase as does income, however it falls slightly in the income range of $90,000 to $170,000 from the previous group.
+The number of not too happy responses is seen to increase as does income, however it falls slightly in the income range of \$90,000 to \$170,000 from the previous group.
 Additionally, very happy marriages are seen to be steadily increasing along with the income.
@@
 From observing @fig-healthincome as income increases so does the number of excellent health responses.
-The three income ranges that fit into the category of below $40,000 all have a relatively low amount of excellent health responses, and a moderate amount of good and fair health.
-However, from the income ranges that include $40,000 and more, the excellent health response is much larger, meanwhile good health occupies the majority of responses.
+The three income ranges that fit into the category of below \$40,000 all have a relatively low amount of excellent health responses, and a moderate amount of good and fair health.
+However, from the income ranges that include \$40,000 and more, the excellent health response is much larger, meanwhile good health occupies the majority of responses.
 Additionally, as income increases the poor health responses are also seen to slightly decrease.
@@
 Ultimately those that have either experienced a better or the same change in wealth are more likely to be either more or less satisfied or pretty well satisfied.
-Meanwhile, whore who have experienced a worse change of wealth have become less satisfied.
+Meanwhile, whore who have experienced a worse change of wealth have become less satisfied.\
 \newpage
@@
 
-According to @fig-finatincome, the majority of respondents who claim that their changes in wealth have gotten better, fall into the $40,000 to $89,999 as well as the $90,000 to $170,000 income ranges.
+According to @fig-finatincome, the majority of respondents who claim that their changes in wealth have gotten better, fall into the \$40,000 to \$89,999 as well as the \$90,000 to \$170,000 income ranges.
 Additionally, a good portion of the respondents in the following two income ranges, claim that their wealth has remained the same, and only a minority believes that their wealth has gotten worse.
-On the other end of the graph, the income groups ranging from $0 to $9,999, $10,000 to $19,999 and $20,000 to $39,000 are all almost fairly equally split between believing that their wealth changes are either better, the same, or worse.
+On the other end of the graph, the income groups ranging from \$0 to \$9,999, \$10,000 to \$19,999 and \$20,000 to \$39,000 are all almost fairly equally split between believing that their wealth changes are either better, the same, or worse.
 
@@
 This bias is interesting, as it demonstrates the sentiment-based nature of the variable of financial satisfaction.
-In this regard, a more accurate survey to probe financial well-being should be targeted towards one’s financial ability to make ends meet.
+In this regard, a more accurate survey to probe financial well-being should be targeted towards one's financial ability to make ends meet.
 
@@
 # 5 Appendix
+
+## 5.1 Survey Link
+
+https://docs.google.com/forms/d/e/1FAIpQLSc9RScig9mAIUceeQA5w4LVJeSN8PfxJNavqAVnnWPrTHeejg/viewform
+
+## 5.2 Survey Questions
+
+![](images/paste-C08F7830.png)
+
+![](images/paste-F617C5EE.png)
+
+![](images/paste-314E528F.png)
+
+![](images/paste-DF7947C0.png)
+
+![![](images/paste-9EB2CCCB.png)](images/paste-0B2CB8F3.png)

### 2023-03-17 scripts/04-test_data.R
test file uploaded

@@ -11,5 +11,70 @@
 #### Workspace setup ####
 library(tidyverse)
 # [...UPDATE THIS...]
+#### Preamble ####
+# Purpose: Tests for simulated data
+# Author: Justin Abando, Jin Di Liu, Marcin Jaczynski
+# Data: 17 March 2023
+# Contact: justin.abando@mail.utoronto.ca
+# Pre-requisites: Requires data from 00-simulate_data.R to be loaded
+# Any other information needed? N/A
+
+
+#### Workspace setup ####
+library(tidyverse)
 
 #### Test data ####
+
+simulated_clean |> #Test to see if there are only 3496 observations
+  count()
+
+head(simulated_clean) #Test to see the first observations
+tail(simulated_clean) #Test to see the final observations
+
+#HAPPY tests
+
+simulated_clean$random_happiness |> #Testing if happiness is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_happiness |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#HAPMAR tests
+
+simulated_clean$random_hapmar |> #Testing if hapmar is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_hapmar |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#HEALTH tests
+
+simulated_clean$random_health |> #Testing if health is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_health |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#FINALTERS tests
+
+simulated_clean$random_finalters |> #Testing if finalters is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_finalters |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#SATFIN tests
+
+simulated_clean$random_satfins |> #Testing if satfin is defined as a character (qualitative)
+  class()
+
+simulated_clean$random_satfins |> #Testing if there is only 3 possible responses to the question
+  unique()
+
+#INCOME16 tests
+
+simulated_clean$new_income_range |> #Testing if income range is defined as a character (qualitative)
+  class()
+
+simulated_clean$new_income_range |> #Test to see if there are 6 unique income ranges from 0 to 170 000 plus others
+  unique()

### 2023-03-17 outputs/paper/paper3.qmd
final final

@@
 ---
-title: "Finances and Individual Well Being"
+title: "An Analysis of the positive effects between Finances and General Well Being."
 author: "Justin Abando, Jin Di Liu, Marcin Jaczynski"
